Meta-analysis of the Interoceptive Accuracy Scale

### 2025-10-31 analysis/study2.qmd
minor

df1a <- cbind(data$df1a, scores$sample1a)
df1b <- cbind(data$df1b, scores$sample1b)
df2 <- cbind(data$df2, scores$sample2)
df3 <- cbind(data$df3, scores$sample3)
df4 <- cbind(data$df4, scores$sample4)
df5 <- cbind(data$df5, scores$sample5)
df6 <- cbind(data$df6, scores$sample6)
df7a <- cbind(data$df7a, scores$sample7a)
df7b <- cbind(data$df7b, scores$sample7b)
df7c <- cbind(data$df7c, scores$sample7c)
df8a <- cbind(data$df8a, scores$sample8a)
df8b <- cbind(data$df8b, scores$sample8b)
df9 <- cbind(data$df9, scores$sample9)
df10 <- cbind(data$df10, scores$sample10)
df11 <- cbind(data$df11, scores$sample11)
df12 <- cbind(data$df12, scores$sample12)
df13 <- cbind(data$df13, scores$sample13)
df14 <- cbind(data$df14, scores$sample14)
df15 <- cbind(data$df15, scores$sample15)
df16 <- cbind(data$df16, scores$sample16)
dff17 <- cbind(data$df17, scores$sample17)

>>>>

df1a <- cbind(data$df1a, scores$sample1a)
df1b <- cbind(data$df1b, scores$sample1b)
df2 <- cbind(data$df2, scores$sample2)
df3 <- cbind(data$df3, scores$sample3)
df4 <- cbind(data$df4, scores$sample4)
df5 <- cbind(data$df5, scores$sample5)
df6 <- cbind(data$df6, scores$sample6)
df7a <- cbind(data$df7a, scores$sample7a)
df7b <- cbind(data$df7b, scores$sample7b)
df7c <- cbind(data$df7c, scores$sample7c)
df8a <- cbind(data$df8a, scores$sample8a)
df8b <- cbind(data$df8b, scores$sample8b)
df9 <- cbind(data$df9, scores$sample9)
df10 <- cbind(data$df10, scores$sample10)
df11 <- cbind(data$df11, scores$sample11)
df12 <- cbind(data$df12, scores$sample12)
df13 <- cbind(data$df13, scores$sample13)
df14 <- cbind(data$df14, scores$sample14)
df15 <- cbind(data$df15, scores$sample15)
df16 <- cbind(data$df16, scores$sample16)
df17 <- cbind(data$df17, scores$sample17)
